Scaffolder - Software for \change{Reproducible}{Manual} Genome Scaffolding.

### 2011-08-14 src/article.tex
fix
Proof read abstract

  \paragraph*{Background:} Assembly of short-read sequencing data can result in
  a fragmented non-contiguous series of genomic sequences. Therefore a common
  step in a genome project is to join neighbouring sequence regions together
  and fill gaps in the assembly using additional sequences. This scaffolding
  step, however, is non-trivial and requires manually editing large blocks of
  nucleotide sequence. Joining these sequences together also hides the source
  of each region in the final genome sequence. Taken together, these
  considerations may make reproducing or editing an existing genome build
  difficult.

  \paragraph*{Methods:} The software outlined here, ``Scaffolder,'' is
  implemented in the Ruby programming language and can be installed via the
  RubyGems software management system. Genome scaffolds are defined using
  YAML - a data format, which is both human and machine-readable. Command line
  binaries and extensive documentation are available.

  \paragraph*{Results:} This software allows a genome build to be defined in
  terms of the constituent sequences using a relatively simple syntax to
  define the scaffold. This syntax further allows  unknown regions to be
  defined, and add additional sequences to fill gaps in the scaffold. Defining
  the genome construction in a file makes the scaffolding process reproducible
  and easier to edit compared with FASTA nucleotide sequence.

>>>>

  \paragraph*{Background:} Assembly of short-read sequencing data can result in
  a fragmented non-contiguous series of genomic sequences. Therefore a common
  step in a genome project is to join neighbouring sequence regions together
  and fill gaps \remove{in the assembly using additional sequences}. This
  scaffolding step, however, is non-trivial and requires manually editing large
  blocks of nucleotide sequence. Joining these sequences together also hides
  the source of each region in the final genome sequence. Taken together, these
  considerations may make reproducing or editing an existing genome build
  difficult.

  \paragraph*{Methods:} The software outlined here, ``Scaffolder,'' is
  implemented in the Ruby programming language and can be installed via the
  RubyGems software management system. Genome scaffolds are defined using YAML
  - a data format\remove{,} which is both human and machine-readable. Command
  line binaries and extensive documentation are available.

  \paragraph*{Results:} This software allows a genome \change{scaffold}{build}
  to be defined in terms of the constituent sequences using a relatively simple
  syntax\remove{to define the scaffold}. This syntax further allows unknown
  regions to be \change{defined}{specified} and add additional sequences to
  fill gaps in the scaffold. Defining the genome construction in a file makes
  the scaffolding process reproducible and easier to edit compared with
  \add{large} FASTA nucleotide sequences.
